### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

\subsection{Performance}

>>>>

\subsection{Performance}
The second limitation of the current side-channel detection tool is the performance bottleneck, especially for those tools based on the symbolic analysis. For example, CaSym can only analyze small programs. CacheD perfroms better. However, it still can not handle large programs like RSA directly. It uses some domain knowledge to analyze only part of the program. The expensive cost comes from the symbolic execution. Symbolic execution can be used to explore all the possible paths, which is useful for many tasks. But it is significantly less likely for cache side channels bugs in crypto primitives. Cryptography primitives are more likely to have an even coverage of different paths (based on pseudo-random cipher states), and a branch-based side channel is vulnerable from the very first branch on secret data, making complex path conditions less often relevant.
